Multi-level Selective Deduplication for VM Snapshots in Cloud Storage

### 2012-03-10 vm_snapshot_sim/2012arch.tex
small change.

\subsection{Snapshot Service Architecture}
%\subsection{Aliyun's VM Cloud and 
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of VMs. A few varieties of mainstream OS are supported.
%including several editions of Windows Server, major Linux distributions, and FreeBSD.
During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
copies the corresponding pre-configured base VM image to her VM as the OS disk, 
and an empty data disk is created and mounted onto her VM as well. 
All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
Aliyun's distributed file system carefully selects the location of primary replica of VM's 
image files such that they are located on the same physical machine of VM instance.
During snapshot backup, concurrent disk write is logged 
so that a  consistent snapshot version  can be derived.

Figure~\ref{fig:arch} shows the architecture view of snapshot service with selective deduplication
at each node. The  snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
In accomplishing such a function, this broker accesses  the snapshot store managed by the underlying distributed file
system.  The inner VM  deduplication is conducted by the broker to access meta data in the snapshot data store
and we discuss this in details in Section~\ref{sect:innerVM}.
The inter-VM deduplication is conducted by the broker to access a  common data block set (CDS) across multiple VMs.
The CDS hash index is stored in the distributed memory cache.

@@

The snapshot store  residing in the distributed file system
supports data access operations  such as \emph{get}, \emph{put} and \emph{delete}.
Other operations include data block traverse  and resource usage  report.
Snapshots are stored  in our distributed file system, just like regular virtual data files. 
A key  difference is that snapshot storage does not need to be
co-located within VM instances and  in fact they can even live in a different cluster to improve the 
data reliability. When a computing cluster is not available, we are still able to  restore users' VMs from another cluster which
contains snapshot backup and run these VMs. 
%to reduce the impact to our users.
%Get interface accepts a piece of data, write it to the underline data file, and return
%a reference to the caller. This reference then can be used in the put interface to
%retrive or delete the data, thus the caller of put interface must preserve the
%data reference for future use. 
%In addition to above standand data access operations, the snapshot service also supports
%\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks of each VM
%in the snapshot store, and quota is used to acknowledge user how much space he
%has actually used.

With Aliyun's distributed file system support, the snapshot store operates 
\emph{append-only} files. Each virtual disk has its own data store, all data 
blocks after deduplication will be stored into that system.
Since all the underline data structures is append only,
upon a delete request, the corresponding data will only be marked rather than being deleted.
A compaction will take place when deleted data has accumulated to a certain threshold, thus 
reclaiming the disk space .

@@

The first-level deduplication is logically localized within each VM.
%There are several reasons that we let each MS have  its own block store for localized duplication rather than sharing. 
%First, all data written to block store are already being processed by deduplication
%process, thus no sharing is necessary unless we want to perform additional deduplication
%inside the block store. Second, 
Such localization increases data independence between different  VM backups,
simplifies  snapshot  management and statistics collection during VM migration and termination,
and facilitates parallel execution of snapshot operations.
%Finally, this reduces the complexity of concurrent snapshot operations.

@@

The inner VM deduplication contains two levels of duplicate detection efforts and the representation of
each snapshot is correspondingly designed as a two-level level index data structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
An image file is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
These blocks are of variable-size, partitioned using
the standard chunking technique~\cite{similar94}.  We use 4KB as the average block size. 
The segment metadata (called segment recipe) records its  content block hashes and  data reference. 
The snapshot-level recipe contains a set of  segment recipes and other meta data information.
\begin{itemize}
\item {\em Level 1 Segment modification  detection}.
If a segment is not changed, indicated by a dirty bit, its content blocks are not changed also. In this case,
 segment-level duplicate detection is more efficient than the block level.

\item {\em Level 2  Block fingerprint comparison.}
If a segment is modified, content blocks of this segment are compared with 
the fingerprints of the existing content blocks within the same segment in
the previous version of this snapshot (called parent  snapshot). Partial duplication
within the segment can be detected and eliminated. 
\end{itemize}

We choose this two-level structure because in practice we observe that at each snapshot there are a large
number of content blocks which are not modified from one snapshot version to another.
Aggregating a large number of content blocks as one segment can significantly
reduce the space cost of snapshot meta data. 
%Namely the  snapshort metadata starts with
%the representation of segment-level meta data. Each segment receipe can be further represented by
%a set of content block receipes.

How can we choose the length of a segment?
Instead of using variables-sized segments, we take a simple approach
to let every segment being aligned to the page boundary of each virtual image file.
For Aliyun, each VM image file is represented as a virtual disk file format
(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual snapshot file 
has been modified or not for segment-level deduplication.
%This is effective because  
%a vhd   file keeps the allocated inner blocks at the same positions until deletion,
%which means the locality of snapshot data is almost natively aligned. 
A dirty bit array is used to indicate which segments have been modified or not. 
Each page (segment) size in our implementation uses 2MB, which contains a large number of content blocks.
%Enforcing a boundary at every 2MB will 
%only break 0.2\% of total data blocks which is tiny.
% dirty bits array. This is because
%Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
%of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
%data segment. During a snapshot operation, we only need to look at the dirty region
%rather than scan over the whold image file, which would be extremely slow.

@@

\subsection{Cross-VM Deduplication with CDS}

The third-level of deduplication is to identify duplicated data blocks among multiple VMs through the index cache
of common data set (CDS).  CDS is the most popular content blocks 
among  recent snapshots across all VMs. 
Each index entry contains  the block fingerprint and a reference pointer to the location of its real content
in the snapshot content block store residing in the underlying distributed file system.
%The structure of CDS meta is not different from the segment recipe we discussed above, 
%except that it is partitioned into many small slices so that each node is easy to load its own slice.

@@

%Behind the scene there is a offline map-reduce job, which will periodically scan the block stores
%in the entire cluster and perform a ``word counting''. High frequency blocks are then added to the CDS if its count 
% is greater than threshold, which is pre-defined by the system memory restrictions.
To control the size of searchable common data in this global setting, we focus on those items that 
are most popular based on the historical snapshot data and the popular analysis is conducted periodically to ensure 
meta data freshness to match the latest data access trend.
There are two advantages to exploit this.
First, a smaller CDS reduces overall resource requirement while covering  most of data blocks in snapshots.
Second a smaller CDS makes the fault tolerance management  easier because we can replicate  more copies
to mitigate the failure.

@@

\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}

\begin{tabular}{cc}
\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
\end{tabular}

\caption{Duplicate count  of common data blocks in a log scale on the left. The right is for common OS blocks.}
\label{fig:zipf-data}
\end{figure}

@@

As the number of VMs increases, the popularity of common blocks for data disks changes.
But this increase has a small impact on OS block popularity because 
there are a limited number of OS releases used by VMs. We let CDS cover the common OS blocks first and
our CDS selection strategy is designed as follows.
\begin{itemize}
\item First, most popular items from OS disks are selected.
Our experiment data shows that about 
100GB data from 7 most popular OS releases
can at least cover over 70\% of OS snapshots and the index of these 100GB OS blocks
only takes about total 1GB in the CDS index and then memory requirement per node 
for duplicate search a large cluster is tiny.
We expect that the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed
OS releases in practice.
\item Second, the degree of duplication is computed for snapshot blocks of data disks and
% and also snapshot 
%blocks of user data items stored in the OS disk (some users store data in their OS disks).
the  most popular items are selected. As discussed in Section~\ref{sect:exper}, 
that about 1\% of data blocks are selected based on their duplicate counts and these popular blocks
can cover about 38\% of data  blocks appeared in various snapshots after level 1 and level deduplication.  
The memory size per node used for CDS is within 150MB.
\end{itemize}
Thus in total the CDS index size per node takes less than 160MB in a large cluster bigger than 100 nodes based on
Aliyun's experiment data, covering over 53\% of blocks in OS and data disks after inner VM deduplication.
This memory usage is well below the limit required by Aliyun.

@@

%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
%
\begin{figure}
  \centering
  \epsfig{file=images/dedup_flow1.eps, height=2in, width=4in}
  \caption{Illustration of snapshot deduplication dataflow.}
  \label{fig:dedupflow}
\end{figure}

@@

\item {\em Block level checkup.}
As shown in Figure~\ref{fig:dedupflow} (b),
for each dirty segment, we divide it into variable-sized blocks,
and compare their signatures with  the corresponding segment recipe in the previous snapshot version (called parent
snapshot). 
For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
\item {\em CDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
Figure~\ref{fig:dedupflow} (d)
shows  a further check to compare  them with  the cached signatures in the CDS by querying
the CDS hash index. If there is a match, the corresponding data pointer from the CDS index is
copied into the segment recipe. 
\item {\em Write new snapshot blocks :}
We continue the previous step and 
if a data block cannot be found in the CDS index, this block is considered to be a new block
and such a block is to be saved in the snapshot block store and  the returned reference  pointer is
saved in the  segment recipe.
\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
 After all segment recipes are saved, the snapshot recipe is complete and can be saved also.
\end{enumerate}

If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
only CDS-based checkup will be conducted.
%This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
%at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.

>>>>

\subsection{Snapshot Service Architecture}
%\subsection{Aliyun's VM Cloud and 
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China 
based on Xen~\cite{Xen2003}. A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of VMs.

A GFS-like distributed file system holds the responsibility of managing physical disk storage
in the cloud. All data needed for VM services, which include runtime VM disk images and snapshot backup data,
reside in this distributed file system.
During the VM creation, a user chooses her flavor of OS distribution and the cloud system 
copies the corresponding pre-configured base VM image to her VM as the OS disk, 
and an empty data disk is created and mounted onto her VM as well. 
All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk at Xen). To avoid network latency and congestion, 
our distributed file system place the primary replica of VM's 
image files at physical machine of VM instance.
During snapshot backup, concurrent disk write is logged 
to ensure a consistent snapshot version is captured.

Figure~\ref{fig:arch} shows the architecture view of our snapshot service
at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
and we discuss this in details in Section~\ref{sect:innerVM}.
The cross-VM deduplication is conducted by the broker to access 
a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
whose block hash index is stored in a distributed memory cache.

@@

The snapshot store 
supports data access operations such as \emph{get}, \emph{put} and \emph{delete}.
Other operations include data block traverse and resource usage report.
The snapshot data does not need to be
co-located with VM instances, and in fact they can even live in a different cluster to improve the 
data reliability: when one cluster is not available, we are still able to restore its VMs from another cluster which
holds its snapshot data. 
%to reduce the impact to our users.
%Get interface accepts a piece of data, write it to the underline data file, and return
%a reference to the caller. This reference then can be used in the put interface to
%retrive or delete the data, thus the caller of put interface must preserve the
%data reference for future use. 
%In addition to above standand data access operations, the snapshot service also supports
%\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks of each VM
%in the snapshot store, and quota is used to acknowledge user how much space he
%has actually used.

Under the hood of snapshot store, it organizes and operates snapshot data 
in the distributed file system. We let each virtual disk has its own snapshot store, 
and no data is shared between
any two snapshot stores, thus achieve great fault isolation. For those selected popular data
that shared by many VM snapshot stores, we could easily increase its availability by having more replications.
%Since all the underline data structures is append only,
%upon a delete request, the corresponding data will only be marked rather than being deleted.
%A compaction will take place when deleted data has accumulated to a certain threshold, thus 
%reclaiming the disk space .

@@

The first-level deduplication is logically localized within each VM.
%There are several reasons that we let each MS have  its own block store for localized duplication rather than sharing. 
%First, all data written to block store are already being processed by deduplication
%process, thus no sharing is necessary unless we want to perform additional deduplication
%inside the block store. Second, 
Such localization increases data independency between different  VM backups,
simplifies  snapshot  management and statistics collection during VM migration and termination,
and facilitates parallel execution of snapshot operations.
%Finally, this reduces the complexity of concurrent snapshot operations.

@@

The inner VM deduplication contains two levels of duplicate detection efforts and the representation of
each snapshot is correspondingly designed as a two-level level index data structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
An image file is divided into a set of segments and each  segment contains hundreds of content blocks from the bottom level.
These blocks are of variable-size, partitioned using
the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
Segment metadata (called segment recipe) records its  content block hashes and data pointers. 
The snapshot recipe contains a list of segments and other meta data information.
\begin{itemize}
\item {\em Level 1 Segment modification  detection}.
If a segment is not changed, indicated by a dirty bit embedded in the virtual disk driver, its content blocks are not changed as well, thus its segment recipe can be simply reused. Operations at this level have almost no cost and most of unmodified data are filtered here.

\item {\em Level 2  Block fingerprint comparison.}
If a segment is modified, we perform fine-grained deduplication using content blocks of this segment to compared with 
the same segment in
the previous snapshot (also called parent snapshot). Partial duplication
within the segment can be detected and eliminated. 
\end{itemize}

We choose this two-level structure because in practice we observe that during each backup period only a small amount
of VM data are added or modified. As the result, even the meat data of two snapshots can be highly similar,
thus aggregating a large number of content blocks as one segment can significantly
reduce the space cost of snapshot meta data. 
%Namely the  snapshort metadata starts with
%the representation of segment-level meta data. Each segment receipe can be further represented by
%a set of content block receipes.

How can we choose the length of a segment?
Instead of using variables-sized segments, we take a simple approach
to let every segment being aligned to the page boundary of each virtual image file.
For Aliyun, each VM image file is represented as a virtual disk file format
(called \emph{vhd} at Xen) and we use a dirty bit to capture if a page (or segment) of a virtual disk file 
has been modified or not to ease the segment-level deduplication.
%This is effective because  
%a vhd   file keeps the allocated inner blocks at the same positions until deletion,
%which means the locality of snapshot data is almost natively aligned. 
A dirty bit array is used to indicate which segments have been modified or not. 
Each page (segment) size in our implementation uses 2MB, which contains a large number of content blocks.
%Enforcing a boundary at every 2MB will 
%only break 0.2\% of total data blocks which is tiny.
% dirty bits array. This is because
%Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
%of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
%data segment. During a snapshot operation, we only need to look at the dirty region
%rather than scan over the whold image file, which would be extremely slow.

@@

\subsection{Cross-VM Deduplication with CDS}
\label{sect:crossVM}

The level-3 deduplication is to identify duplicated data blocks among multiple VMs through the index cache
of common data set (CDS).  CDS is the most popular content blocks 
among snapshots across all VMs. 
Each index entry contains  the block fingerprint and a reference pointer to the location of its real content
in the snapshot content block store.
%The structure of CDS meta is not different from the segment recipe we discussed above, 
%except that it is partitioned into many small slices so that each node is easy to load its own slice.

@@

%Behind the scene there is a offline map-reduce job, which will periodically scan the block stores
%in the entire cluster and perform a ``word counting''. High frequency blocks are then added to the CDS if its count 
% is greater than threshold, which is pre-defined by the system memory restrictions.
To control the size of searchable common data in this global setting, we focus on those items that 
are most popular based on the historical snapshot data and the popular analysis is conducted periodically to ensure 
meta data freshness to match the latest data access trend.
There are two advantages to exploit this.
First, a smaller CDS reduces overall resource requirement while covering most of data duplication.
Second, knowing this small set of data is shared heavily makes the fault tolerance management 
easier because we can replicate more copies to mitigate the failure.

@@

\begin{figure}[htbp]
\centering
\epsfig{file=images/vector.eps, width=3.2in}
%\epsfig{file=images/log-log.disk.eps, width=3in}

%\begin{tabular}{cc}
%\epsfig{file=images/datadisk.count_rank.eps, width=1.5in} &
%\epsfig{file=images/35vmos.count-rank.eps,width=1.5in}
%\end{tabular}

\caption{Number of duplicates vesus ranking}
\label{fig:zipf-data}
\end{figure}

@@

As the number of VMs increases, the popularity of common blocks for data disks changes.
But this increase has a small impact on OS block popularity because 
there are a limited number of OS releases used by VMs. We let CDS cover the common OS blocks first and
our CDS selection strategy is designed as follows.
\begin{itemize}
\item First, most popular items from OS disks are selected as the initial CDS.
Our experiment data shows that about 
100GB data from 7 most popular OS releases
can at least cover over 70\% of OS snapshots and the index of these 100GB OS blocks
only takes about total 1GB in the CDS index and then memory requirement per node 
for duplicate search a large cluster is tiny.
We expect that the OS CDS index may grow up to 2GB in order to cover large varieties  of commonly deployed
OS releases in practice.
\item Second, the degree of duplication is computed for the rest of blocks in snapshot store, and
% and also snapshot 
%blocks of user data items stored in the OS disk (some users store data in their OS disks).
the  most popular items are selected. As discussed in Section~\ref{sect:exper}, 
that about 1\% of data blocks are selected based on their duplicate counts and these popular blocks
can cover about 38\% of data  blocks appeared in various snapshots after level 1 and level deduplication.  
The memory size per node used for CDS is within 150MB.
\end{itemize}
Thus in total the CDS index size per node takes less than 160MB in a large cluster bigger than 100 nodes based on
Aliyun's experiment data, covering over 53\% of blocks in OS and data disks after inner-VM deduplication.
This memory usage is well below the limit required by our VM services.

@@

%%Our deduplication process is divided into three levels, at each level, we eliminate the most of duplicate data with available knowledge, preventing them from going further because deduplication at deeper level is more expensive.
%
\begin{figure}
  \centering
  \epsfig{file=images/dedup_flow1.eps, height=2in, width=3.5in}
  \caption{Illustration of snapshot deduplication dataflow.}
  \label{fig:dedupflow}
\end{figure}

@@

\item {\em Block level checkup.}
As shown in Figure~\ref{fig:dedupflow} (b),
for each dirty segment, we divide it into variable-sized blocks,
and compare their signatures with  the corresponding segment recipe in the previous snapshot version (called parent
snapshot). 
For any duplicated block, we copy the data pointer directly from the parent segment recipe. 
\item {\em CDS checkup.} For the remaining  content blocks whose duplicate status is unknown,
Figure~\ref{fig:dedupflow} (d)
shows  a further check to compare  them with  the cached signatures in the CDS by querying
the CDS hash index. If there is a match, the corresponding data pointer from the CDS index is
copied into the segment recipe. 
\item {\em Write new snapshot blocks :}
We continue the previous step and 
if a data block cannot be found in the CDS index, this block is considered to be a new block
and such a block is to be saved in the snapshot block store and  the returned data pointer is
saved in the  segment recipe.
\item {\em Save recipes.} Finally the  segment recipes are saved in the  snapshot block store also.
 After all segment recipes are saved, the snapshot recipe is complete and can be saved finally.
\end{enumerate}

If there is no parent snapshot available, which happens when a VM creates its first snapshot, 
only CDS-based checkup will be conducted. 
Most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.
%This is important because most of the cross-VM duplication, such as OS related data and popular software data, is eliminated
%at this stage. Later snapshot will very likely find these data are not changed and simply copy the data pointers from parent snapshot.

### 2012-03-10 vm_snapshot_sim/2012background.tex
small change.

One weakness the hasn't been addressed by previous solutions is that we want to isolate 
each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
to affect large amount of VMs due to data sharing.

@@

We discuss the characteristics and 
main requirements for VM snapshot backup in a cloud environment.
which are different from a traditional data backup. 
% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{enumerate}
\item {\em Cost consciousness.}
There are tens of thousands of VMs running on a large-scale cluster. 
The amount of data to backup is so huge such that 3rd-party solutions are generally not affordable.
On the other hand, the computing resources allocated for snapshot service is very limited
because VM performance has higher priority.  
At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
the memory footprint of snapshot service should not exceed 500MB at each node.

@@

There are multiple choices in designing a backup architecture  for VM snapshots.
We discuss the following design options with a consideration on their strengths and weakness.
\begin{enumerate}
\item  {\em An external and dedicated backup storage system.} 
In this architecture setting, a separate backup storage system using
the standard backup and deduplication techniques can be deployed~\cite{bottleneck08,extreme_binning09,sparseindex09}. 
This system is attached to the cloud network and every machine can periodically transfer snapshot data to 
the attached backup system. 
A key weakness of this approach is communication bottleneck between a large number of machines
in a cloud to this centralized  service.
Another weakness is that the cost of allocating separate resource for dedicated backup  can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup cluster may not be fully utilized.
\item {\em A decentralized and co-hosted backup system with full deduplication.}
In this option, the backup system runs on an existing set of cluster machines.
% and a distributed storage architecture for backup allows a possible exploitation of  data locality between
%the source of data and storage location of backup data. 
The disadvantage is that 
%the backup service would compete CPU, memory, and disk resources with the other cloud services.
even such a  backup service may only use  a fraction of the existing disk storage, 
fingerprint-based search does require a significant amount of memory for fast lookup of identical content chunks.
This competes memory resource  with the existing applications.
%Decentralized deduplication is studied in ~\cite{Clements2009} and the focus is on
%block-level copy-on-write and compare-by-value techniques.

Even approximation~\cite{extreme_binning09,sparseindex09} can be used to reduce memory requirement,  
a  key weakness of global content fingerprint comparison is that it can affect fault isolation.
Because a content chunk is compared with a content signature collected from other users,
this artificially creates data dependence among different cloud users.
% since storage for shared identical content chunks can become a failure point.
The loss of a common chunk can affect many users whose VM images share this 
chunk. Adding replicas for this global dataset can enhance the availability,
but incurs significantly more cost.
%2) data sharing among users for accessing common signagutes causes the system less resilient to storage failures.
%any loss of one piece of  shared data content hash and actualcontent will damange many VM snapshots, which can cause massive impacts
%on reliability of many users.

@@

With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
deduplication. This service is hosted   in the existing set of machines and resource usage is controlled
with a minimal impact to the existing applications.
The duplication process is first conducted among data within each VM
and then is conducted  across VMs to utilize a common dataset.  
Given the concern that searching duplicates across  VMs  is a global feature which can affect parallel performance
and complicate failure management,
we would like to use a small common dataset while still maintaining a cost-effective deduplication ratio.
For this purpose, we exploit the data characteristics of snapshots and only store most popular data.
%
%in the  our studies show that there are a large amount of data unmodified in VM snapshots
%and shared among many users (e.g. OS data). The sharing pattern follows a zip-like distribution.
%With this characteristic, we can store a small amount of popular data items which coverage a large amount of
%snapshot data blocks. 
%We discuss our design and data analysis in the next section.

>>>>

@@

We discuss the characteristics and 
main requirements for VM snapshot backup in a cloud environment.
which are different from a traditional data backup. 
% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{enumerate}
\item {\em Cost consciousness.}
There are tens of thousands of VMs running on a large-scale cluster. 
The amount of data is so huge such that backup cost must be controlled carefully.
On the other hand, the computing resources allocated for snapshot service is very limited
because VM performance has higher priority.  
At Aliyun, it is required that while CPU and disk usage should be small or modest during backup time,
the memory footprint of snapshot service should not exceed 500MB at each node.

@@

There are multiple choices in designing a backup architecture  for VM snapshots.
We discuss the following design options with a consideration on their strengths and weakness.
\begin{enumerate}
\item  {\em An external and dedicated backup storage system.} 
In this architecture setting, a separate backup storage system using
the standard backup and deduplication techniques can be deployed~\cite{bottleneck08,extreme_binning09,sparseindex09}. 
This system is attached to the cloud network and every machine can periodically transfer snapshot data to 
the attached backup system. 
A key weakness of this approach is communication bottleneck between a large number of machines
in a cloud to this centralized  service.
Another weakness is that the cost of allocating separate resource for dedicated backup  can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup cluster may not be fully utilized.
\item {\em A decentralized and co-hosted backup system with full deduplication.}
In this option, the backup system runs on an existing set of cluster machines.
% and a distributed storage architecture for backup allows a possible exploitation of  data locality between
%the source of data and storage location of backup data. 
The disadvantage is that 
%the backup service would compete CPU, memory, and disk resources with the other cloud services.
even such a  backup service may only use  a fraction of the existing disk storage, 
fingerprint-based search does require a significant amount of memory for fingerprint lookup of searching duplicates.
This competes memory resource  with the existing VMs.
%Decentralized deduplication is studied in ~\cite{Clements2009} and the focus is on
%block-level copy-on-write and compare-by-value techniques.

Even approximation~\cite{extreme_binning09,sparseindex09} can be used to reduce memory requirement,
one key weakness the hasn't been addressed by previous solutions is that global content sharing affects
fault isolation.
Because a content chunk is compared with a content signature collected from other users,
this artificially creates data dependency among different VM users.
% since storage for shared identical content chunks can become a failure point.
In large scale cloud, node faiures happen at daily basis,
the loss of a shared block can affect many users whose snapshots share this 
data block. 
Without any control of such data sharing, we can only increase  
replication for global dataset to enhance the availability,
but this incurs significantly more cost.

%we want to isolate 
%each VM's snapshot backup as much as possible while still enjoy the benefit of deduplication.
%In large scale cloud, node faiures happen at daily basis, we don't want a problem at small scale
%to affect large amount of VMs due to data sharing.
%a key weakness of global content fingerprint comparison is that it affects fault isolation.

%2) data sharing among users for accessing common signagutes causes the system less resilient to storage failures.
%any loss of one piece of  shared data content hash and actualcontent will damange many VM snapshots, which can cause massive impacts
%on reliability of many users.

@@

With these considerations in mind, we propose a decentralized backup architecture with multi-level and selective 
deduplication. This service is hosted   in the existing set of machines and resource usage is controlled
with a minimal impact to the existing applications.
The deduplication process is first conducted among snapshots within each VM
and then is conducted across VMs.  
Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
and complicate failure management,
we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance.
%
%in the  our studies show that there are a large amount of data unmodified in VM snapshots
%and shared among many users (e.g. OS data). The sharing pattern follows a zip-like distribution.
%With this characteristic, we can store a small amount of popular data items which coverage a large amount of
%snapshot data blocks. 
%We discuss our design and data analysis in the next section.
